Tables with \textbf{xtable} and \textbf{knitr}

### 2016-11-01 src/ArticleReadyTableGenerate.Rnw
finished pooled LCDM removed extra printouts

<<LoadData_and_BasicDataMunge,echo=FALSE,results='hide',warning=FALSE, message=FALSE,cache=FALSE>>=
# Load Data
library(foreign)
library(dplyr)
library(xtable)
HOME_DIR <- Sys.getenv("HOME")
print(HOME_DIR)
opts_knit$set(root.dir=paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/",sep="",collapse=""))
#setwd("./projects/MAS_Score_Analysis")
#setwd( paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/"))
#The script gets data from  SPSS files, merges data frames to one data frame
source( paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/","./src/MAS_MCIsubtype_analysis.R",sep="",collapse=""))
all.df<- droplevels(all.df)

@@

<<ICVStats,eval=TRUE,error=TRUE,echo=FALSE>>=
require(car)
aov.fit<- lm(ICV_W1~YrsEd+age+sex+Diag,data=all.df)
aov.result.type3 <- Anova(aov.fit,type="III")
aov.result <- aov(aov.fit)
# Does ICV show a trend level  group difference (Is p-value for Diag sig?)
print("ICVStats ANOVA with covars")
print(aov.result.type3)

# Does ICV show a trend level  group difference (Is p-value for Diag sig?)
print("ICVStats ANOVA")
print(aov.result)

@@

<<ICVStats_plot,  eval=TRUE,echo=FALSE>>=
summary_table_2.df  <- summarize (grouping_gender_diag, mean_ICV=mean(ICV_W1,na.rm=T), sd_ICV=sd(ICV_W1,na.rm=T))

@@

aov.result.summary <- summary(aov.result)
if (!is.data.frame(aov.result.summary)){
aov.result.summary  <- aov.result.summary[[1]]
}
print(table.out, include.rownames=FALSE,include.colnames=TRUE)

p_vals <- formatC(aov.result.summary$`Pr(>F)` [1:3], digits = 3,drop0trailing=TRUE)
print (aov.result.summary)
Covariate_names <- rownames(aov.result.summary)[1:3]
print(str(aov.result.summary))
print(Covariate_names)
cov_column <- paste(Covariate_names,"(p = ",p_vals,")",sep="")
cov_column <- c(cov_column,rep("",2))
cov_column_2 <-c ("", paste("p = ",aov.result.summary$`Pr(>F)` [4],")",sep=""),"")
cov_column_2 <- c(cov_column_2,rep("",2))

@@

@@

<<subregion_sideway_table_summary_stats,eval=TRUE,echo=FALSE>>=
stat.tables.for.regions <- list()
summ.stats.tables<-list(stg=list(),mtg=list(),itg=list(),postcing=list(),antcing=list())
for (region.for.table in c("stg" ,"mtg","itg","postcing","antcing")){
  all.df.lf.stg    <- filter(all.df.lf, region==region.for.table)

@@

  all.df.lf.stg.lh.grp<- group_by(all.df.lf.stg.lh, aggstat, sex,Diag)
  all.df.lf.stg.rh.grp<- group_by(all.df.lf.stg.rh, aggstat, sex,Diag)

@@

}
print(str(summ.stats.tables))
@

@@

print(paste0("Diagnostics for Subregion = ",region.for.table," ",
             measure.name ))
    all.df.lf.stg    <- filter(all.df.lf, region==region.for.table & aggstat==measure.name)
all.df.lf.stg <- setupAnova(all.df.lf.stg)

@@

        covar.col <- rep("",5)
        pval.col <- rep("",5)
        if (num.sig.vars==0) {
          covar.col[1]<- "None"
        }
        else {
          covar.col[1:num.sig.vars] <- sig.covar.table.col
          covar.col[(num.sig.vars+1):5]<-""
        }
        p.vals <- formatC(p.vals, digits = 3,drop0trailing=TRUE)
        pval.col[1]  <-  formatC(p.value.for.Diag, digits = 3,drop0trailing=TRUE)
        unit.block <- data.frame(sex=sex.var,aggstat=agg.stat.name, Diag=diag.list ,Covariates=covar.col,p_values= pval.col)
        aov.test.results <- rbind(aov.test.results,unit.block)
        covar.col.all.sex <- c(covar.col.all.sex,covar.col)
        pval.col.all.sex  <- c(pval.col.all.sex,pval.col)
      }
    }
    print(covar.col.all.sex )
    print(pval.col.all.sex )
    print.table.df <- merge(print.table.rh.df,print.table.lh.df,
                        by = c("aggstat","sex","Diag"),sort=FALSE)
    print.table.merged.df<- merge(print.table.df, aov.test.results,
                                    by = c("aggstat","sex","Diag"),
                                  sort=FALSE )

@@

  print (str(pool_stat_tests_all_regions_sides))
  #pool_stats_all <-  matrix(nrow=2,ncol=5,dimnames = list(sides=sides,regions=regions))
  #pool_stats_all <- list(NULL, names=)
  for ( side in sides) {

@@

      #read the pooled files
      for (i in 1:5) {
        cond_fileh <- paste(DATA_DIR,"/",side,'_',region,"_", conditions[i],
                            "_wave1_pooled_antsy.txt", sep="", collapse ="")
        print (cond_fileh)
        if (! file.exists(cond_fileh)) {
          print (paste0( cond_fileh,
                         " does not exist",sep="",collapse="") )
        }
        #pooled_stats <-read.table(file=cond_fileh, nrows = 2.5E6, colClasses = "numeric")
        pooled_stats <- scan(file=cond_fileh)
        print (str(pooled_stats_list))
        if ( is.data.frame(pooled_stats_list) ) {
          pooled_stats <- as.vector(pooled_stats[,1])
        }
        pooled_stats_list <-c(pooled_stats_list,list(pooled_stats))
      }
      #print(str(pool_stats_all[side,region]))
      #print(str(pooled_stats_list))
      #pool_stats_all[side,region] <- c(pool_stats_all[side,region],pooled_stats_list)
      #pool_stats_all[side,region] <- pooled_stats_list

@@

\begin{table}[t]
  \centering
	\begin{tabular}{rrrrrrr}
		\hline

<<echo=FALSE, results='asis' >>=
 convert_to_paper_style <- function(x) {
   if (x<1E-4) {
   return ("<0.0001") 
   } else {
    return (format(x,digits=4))
   }
 }
  simp.colnames<- function(x) {
     y = lapply(x,strsplit,"_",fixed=TRUE)
     #return(y)
     z = sapply(y , function(l) l[[1]][[1]])
     #z = gsub(".", " ",y)
    return (z)
  }
  make_matrix_printable <- Vectorize(convert_to_paper_style)
  cond_1 = conditions[comparisons[,1]]
  cond_2 = conditions[comparisons[,2]]
  comparison_strings <- paste(cond_1,cond_2, sep =" vs ")
  test_names <- c("KS test","MWU test", "Welch's t-test")
  col_names <- outer(hypothesis_ordinality,test_names,paste,  sep="_")
  p_value_table_names <-expand.grid(comparison_strings, col_names)
  p_value_table <- matrix(0,nrow = 7,ncol = 9)
  p_val_table_list<-list()
  xtablelist<- list()
  for (side in sides){
    for ( i in 1:7 ) {
      for (j in 1:3){
        test.type <-  hypothesis_ordinality[j]
        for (k in 0:2){
          test.name <- names(pooled_test_results[[i]][[test.type]][(k+1)])
        p_value_table[i,j + (k*3)] <- pooled_test_results[[i]][[test.type]][[test.name]]$p.value

@@

  }
   attr(p_val_table_list, "subheadings") <- paste0("Hemisphere : ",names(p_val_table_list))
   xtablelist <- xtableList(p_val_table_list)
  addtorow <- list()
  addtorow$pos <- list(-1)
  addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
  print.xtableList (xtablelist, add.to.row = addtorow, only.contents=FALSE,
    include.rownames=TRUE, sanitize.colnames.function = simp.colnames,
    type="latex")
# create a table of 7 comparisons

@@

\newpage
\begin{sidewaystable}
	\centering
	\footnotesize
	\begin{tabular}{rr|rrr|rrr|rrr}
		\hline
		\multicolumn{2}{c|}{Region} \T\B & \multicolumn{3}{c|}{KS test} & \multicolumn{3}{c|}{MWU test} & \multicolumn{3}{c}{Welch's t-test} \\
		& & two-sided & less & greater & two-sided & greater & less & two-sided & greater & less \\ \hline
		& aMCI vs norm\T & $<$.0001 & .0832 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		rh stg & nMCI vs norm & $<$.0001 & $<$.0001 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI\T & $<$.0001 & .5210 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
		& aMCI vs norm & $<$.0001 & .9794 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		lh stg & nMCI vs norm & $<$.0001 & .9983 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & $<$.0001 & $<$.0001 & .0128 & .0064  & .9936 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & $<$.0001 & $<$.0001 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		rh stg & nMCI vs norm & $<$.0001 & .0121 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		(women)& aMCI vs nMCI & $<$.0001 & $<$.0001 & .0086 & .1065 & .0533 & .9467 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & $<$.0001 & .9989 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		lh stg & nMCI vs norm & $<$.0001 & .9998 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		(women)& aMCI vs nMCI & $<$.0001 & $<$.0001 & .0032 & .0060 & .0030 & .9970 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & $<$.0001 & .0396 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		rh mtg & nMCI vs norm & $<$.0001 & $<$.0001 & $<$.0001 & .5428 & .7286 & .2714 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & .4099 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
		& aMCI vs norm\T & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		lh mtg & nMCI vs norm & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1  & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & .0296 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
		& aMCI vs norm\T &  $<$.0001 & $<$.0001 & $<$.0001 & .5723 & NA & NA & .8289 & NA & NA \\
		rh itg & nMCI vs norm & $<$.0001 & $<$.0001 & .7620 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
		& aMCI vs nMCI & $<$.0001 & .5502 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\ \hline
		& aMCI vs norm\T &  $<$.0001 & .8740 & $<$.0001 &  $<$.0001 & 1 & $<$.0001 &  $<$.0001 & 1 & $<$.0001 \\
		lh itg & nMCI vs norm & $<$.0001 & .7938 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & .8740 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
	\end{tabular}
	\caption{\textbf{Temporal Lobe Pooled LCDM Analysis Results.}  Showing p-values obtained from nonparametric distribution tests.}
	\label{Wave1.TL.nonpara}
\end{sidewaystable}

\newpage
\begin{sidewaystable}
	\centering
	\footnotesize
	\begin{tabular}{rr|rrr|rrr|rrr}
		\hline
		\multicolumn{2}{c|}{Region} \T\B & \multicolumn{3}{c|}{KS test} & \multicolumn{3}{c|}{MWU test} & \multicolumn{3}{c}{Welch's t-test} \\
		& & two-sided & less & greater & two-sided & greater & less & two-sided & greater & less \\ \hline
		& aMCI vs norm\T &  $<$.0001 & $<$.0001 & .9896 &  $<$.0001 & $<$.0001 & 1 &  $<$.0001 & $<$.0001 & 1 \\
		rh antcing & nMCI vs norm & .0047 & .0024 & .9696 & .0496 & .0248 & .9752 & .0463 & .0232 & .9768 \\
		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .9986 & $<$.0001 & $<$.0001 & .9986 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & $<$.0001 & $<$.0001 & .8789 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
		lh antcing & nMCI vs norm & $<$.0001 & $<$.0001 & .6552 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .9725 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & .0001 & $<$.0001 & .0043 & .2136 & .1068 & .8932 & .5986 & .2993 & .7007 \\
		rh postcing & nMCI vs norm & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .9786 & $<$.0001 & $<$.0001 & .9786 & $<$.0001 & $<$.0001 & 1 \\ \hline
		& aMCI vs norm\T & $<$.0001 & .9911 & $<$.0001 & $<$.0001 & 1 & $<$.0001  & $<$.0001 & 1 & $<$.0001  \\
		lh postcing & nMCI vs norm & $<$.0001 & .9971 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 & $<$.0001 \\
		& aMCI vs nMCI & $<$.0001 & $<$.0001 & .8553 & $<$.0001 & $<$.0001 & 1 & $<$.0001 & $<$.0001 & 1 \\
	\end{tabular}
	\caption{\textbf{Cingulate Gryus Pooled LCDM Analysis Results}   Showing p-values obtained from nonparametric distribution tests.}
	\label{Wave1.cing.nonpara}
\end{sidewaystable}

>>>>

<<LoadData_and_BasicDataMunge,echo=FALSE,results='hide',warning=FALSE, message=FALSE,cache=FALSE>>=
# Load Data
library(foreign)
library(dplyr)
library(xtable)
HOME_DIR <- Sys.getenv("HOME")
#print(HOME_DIR)
opts_knit$set(root.dir=paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/",sep="",collapse=""))
#setwd("./projects/MAS_Score_Analysis")
#setwd( paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/"))
#The script gets data from  SPSS files, merges data frames to one data frame
source( paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/","./src/MAS_MCIsubtype_analysis.R",sep="",collapse=""))
all.df<- droplevels(all.df)

@@

<<ICVStats,eval=TRUE,error=TRUE,echo=FALSE,results="hide">>=
require(car)
aov.fit<- lm(ICV_W1~YrsEd+age+sex+Diag,data=all.df)
aov.result.type3 <- Anova(aov.fit,type="III")
aov.result <- aov(aov.fit)
# Does ICV show a trend level  group difference (Is p-value for Diag sig?)
#print("ICVStats ANOVA with covars")
#print(aov.result.type3)

# Does ICV show a trend level  group difference (Is p-value for Diag sig?)
#print("ICVStats ANOVA")
#print(aov.result)

@@

<<ICVStats_plot,  eval=TRUE,echo=FALSE,results="asis">>=
summary_table_2.df  <- summarize (grouping_gender_diag, mean_ICV=mean(ICV_W1,na.rm=T), sd_ICV=sd(ICV_W1,na.rm=T))

@@

aov.result.summary <- summary(aov.result)
if (!is.data.frame(aov.result.summary)){
aov.result.summary  <- aov.result.summary[[1]]
}

p_vals <- formatC(aov.result.summary$`Pr(>F)` [1:3], digits = 3,drop0trailing=TRUE)
#print (aov.result.summary)
Covariate_names <- rownames(aov.result.summary)[1:3]
#print(str(aov.result.summary))
#print(Covariate_names)
cov_column <- paste(Covariate_names,"(p = ",p_vals,")",sep="")
cov_column <- c(cov_column,rep("",2))
cov_column_2 <-c ("", paste("p = ",aov.result.summary$`Pr(>F)` [4],")",sep=""),"")
cov_column_2 <- c(cov_column_2,rep("",2))

@@

print(table.out, include.rownames=FALSE,include.colnames=TRUE)
@

@@

<<subregion_sideway_table_summary_stats,eval=TRUE,echo=FALSE>>=
#print("subregion_sideway_table_summary_stats")
stat.tables.for.regions <- list()
summ.stats.tables<-list(stg=list(),mtg=list(),itg=list(),postcing=list(),antcing=list())
for (region.for.table in c("stg" ,"mtg","itg","postcing","antcing")){
  all.df.lf.stg    <- filter(all.df.lf, region==region.for.table)

@@

  all.df.lf.stg.lh$aggstat<- as.factor(all.df.lf.stg.lh$aggstat)
  all.df.lf.stg.lh.grp<- group_by(all.df.lf.stg.lh, aggstat, sex,Diag)
  all.df.lf.stg.rh.grp<- group_by(all.df.lf.stg.rh, aggstat, sex,Diag)

@@

}
#print(str(summ.stats.tables))
@

@@

print(paste0("Diagnostics for Subregion = ",region.for.table," ",
             measure.name ))
    print(names(all.df.lf))
    all.df.lf.stg    <- filter(all.df.lf, region==region.for.table & aggstat==measure.name)
all.df.lf.stg <- setupAnova(all.df.lf.stg)

@@

        covar.col <- rep("",5)
        pval.col <- rep("",5)
        if (num.sig.vars==0) {
          covar.col[1]<- "None"
        }
        else {
          covar.col[1:num.sig.vars] <- sig.covar.table.col
          covar.col[(num.sig.vars+1):5]<-""
        }
        p.vals <- formatC(p.vals, digits = 3,drop0trailing=TRUE)
        pval.col[1]  <-  formatC(p.value.for.Diag, digits = 3,drop0trailing=TRUE)
        unit.block <- data.frame(sex=sex.var,aggstat=agg.stat.name, Diag=diag.list ,Covariates=covar.col,p_values= pval.col)
        aov.test.results <- rbind(aov.test.results,unit.block)
        covar.col.all.sex <- c(covar.col.all.sex,covar.col)
        pval.col.all.sex  <- c(pval.col.all.sex,pval.col)
      }
    }
    #print(covar.col.all.sex )
    #print(pval.col.all.sex )
    print.table.df <- merge(print.table.rh.df,print.table.lh.df,
                        by = c("aggstat","sex","Diag"),sort=FALSE)
    print.table.merged.df<- merge(print.table.df, aov.test.results,
                                    by = c("aggstat","sex","Diag"),
                                  sort=FALSE )

@@

  #print (str(pool_stat_tests_all_regions_sides))
  #pool_stats_all <-  matrix(nrow=2,ncol=5,dimnames = list(sides=sides,regions=regions))
  #pool_stats_all <- list(NULL, names=)
  for ( side in sides) {

@@

      #read the pooled files
      for (i in 1:5) {
        cond_fileh <- paste(DATA_DIR,"/",side,'_',region,"_", conditions[i],
                            "_wave1_pooled_antsy.txt", sep="", collapse ="")
        #print (cond_fileh)
        if (! file.exists(cond_fileh)) {
          print (paste0( cond_fileh,
                         " does not exist",sep="",collapse="") )
        }
        #pooled_stats <-read.table(file=cond_fileh, nrows = 2.5E6, colClasses = "numeric")
        pooled_stats <- scan(file=cond_fileh)
        #print (str(pooled_stats_list))
        if ( is.data.frame(pooled_stats_list) ) {
          pooled_stats <- as.vector(pooled_stats[,1])
        }
        pooled_stats_list <-c(pooled_stats_list,list(pooled_stats))
      }
      #print(str(pool_stats_all[side,region]))
      #print(str(pooled_stats_list))
      #pool_stats_all[side,region] <- c(pool_stats_all[side,region],pooled_stats_list)
      #pool_stats_all[side,region] <- pooled_stats_list

@@

<<echo=FALSE, results='asis',cache=FALSE >>=
 convert_to_paper_style <- function(x) {
   if (x<1E-4) {
   return ("<0.0001") 
   } else {
    return (format(x,digits=4))
   }
 }
  simp.colnames<- function(x) {
     y = lapply(x,strsplit,"_",fixed=TRUE)
     #return(y)
     z = sapply(y , function(l) l[[1]][[1]])
     #z = gsub(".", " ",y)
    return (z)
  }
  make_matrix_printable <- Vectorize(convert_to_paper_style)
  cond_1 = conditions[comparisons[,1]]
  cond_2 = conditions[comparisons[,2]]
  comparison_strings <- paste(cond_1,cond_2, sep =" vs ")
  test_names <- c("KS test","MWU test", "Welch's t-test")
  col_names <- outer(hypothesis_ordinality,test_names,paste,  sep="_")
  p_value_table_names <-expand.grid(comparison_strings, col_names)
  @

<<echo=FALSE, results='asis',cache=FALSE >>=
  for (region in regions) { 
  p_value_table <- matrix(0,nrow = 7,ncol = 9)
  p_val_table_list<-list()
  xtablelist<- list()
  for (side in sides){

    pooled_test_results = pool_stat_tests_all_regions_sides[side,region][[1]]
    for ( i in 1:7 ) {
      for (j in 1:3){
        test.type <-  hypothesis_ordinality[j]
        for (k in 0:2){
          test.name <- names(pooled_test_results[[i]][[test.type]][(k+1)])
        p_value_table[i,j + (k*3)] <- pooled_test_results[[i]][[test.type]][[test.name]]$p.value

@@

  }
   attr(p_val_table_list, "subheadings") <- paste0("Hemisphere : ",c("Left","Right"))
   xtablelist <- xtableList(p_val_table_list, caption = paste0("Hypothesis Tests based on pooled LCDM statistics for ",region,collapse= ""))
   col.names <- c("KS test","MWU test", "Welch's t-test")
   # Region & \multicolumn{3}{l}{KS test} & \multicolumn{3}{l}{MWU test} & \multicolumn{3}{l}{Welch's t-test}\\
  rowcom <- list()
  rowcom$pos = list(-1)
  rowcom$command = paste0(paste0("Region",paste0(" & \\multicolumn{3}{c}{", col.names , '}', collapse=''),collapse=''), '\\\\')
  #print(addtorow)
  print(xtablelist, add.to.row = rowcom, only.contents=FALSE,
    include.rownames=TRUE, sanitize.colnames.function = simp.colnames,
    type="latex",floating.environment = "sidewaystable")
  }

# create a table of 7 comparisons

@@
